Scheduling and Amortization for MPC

### 2022-01-30 paper_SIMD.tex
(Draft) extension of Basic vectorization for handling of targetless phi-nodes.

\FOR {each dimension $d$ from highest to 0}
\FOR {each $\phi$-node $n$ in loop $i_1,...,i_d$}
\STATE {compute $\mathit{closure}(n)$}
\WHILE {there are closure $cl_1$ and $cl_2$ that intersect}
\STATE {merge $cl_1$ and $cl_2$}
\ENDWHILE
\FOR {each closure $cl$ (after merge)}
\STATE {create FOR $i_d = 0; ...$ loop}
\STATE {add $\phi$-nodes in $cl$ to header block}
\STATE {add statements in $cl$ to loop body in some order of dependences}
\STATE \COMMENT {Dimension is not vectorizable: }
\STATE {change $\stackrel{\rightarrow}{i_d}$ to $i_d$ in all statements in loop}
\STATE {treat FOR loop as monolith node: change def-use edges accordingly. Some edges become same-level.}
\ENDFOR
\ENDFOR
\ENDFOR

>>>>

\FOR {each dimension $d$ from highest to 0}
\FOR {each $\phi$-node $n$ in loop $i_1,...,i_d$}
\STATE {compute $\mathit{closure}(n)$}
\ENDFOR

\COMMENT {{\color{red} $cl_1$ and $cl_2$ intersect if they have common statement, or update same array; "intersect" definition can be expanded}}

\WHILE {there are closure $cl_1$ and $cl_2$ that intersect}
\STATE {merge $cl_1$ and $cl_2$}
\ENDWHILE
\FOR {each closure $cl$ (after merge)}
\STATE {create FOR $i_d = 0; ...$ loop}
\STATE {add $\phi$-nodes in $cl$ to header block}
\STATE {{\color{red}{add target-less $\phi$-node for A if $cl$ updates array A}}}
\STATE {add statements in $cl$ to loop body in some order of dependences}
\STATE \COMMENT {Dimension is not vectorizable: }
\STATE {change $\stackrel{\rightarrow}{i_d}$ to $i_d$ in all statements in loop}
\STATE {treat FOR loop as monolith node: change def-use edges accordingly. Some edges become same-level.}
\ENDFOR
{
\color{red}
\FOR {each target-less $\phi$-node $A_1 = \phi(A_0,A_k)$}
\STATE {in vectorizable stmts, replace use of $A_1$ with $A_0$}
\STATE {discard $\phi$-node if not used in any $cl$}
\ENDFOR
}
\ENDFOR
